Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-09 supplement.tex

\title{Supplement: Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b}

@@

\section{Introduction}
\citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
KIC 12557548's (hereafter \shStar's) light curve exhibits periodic flux dips with a period of 0.653 days.
Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
The amplitudes of the flux dips are highly stochastic and unpredictable from one event to the next 0.653 days later.
This indicates the creation and clearing of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
These unusual light curve behaviors are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
The \shStar\ system has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.

@@

>>>>

\title{Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b}

@@

\section{Introduction}

Supplementary Material/Notes for the main paper

\section{Observations}

\citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
KIC 12557548's (hereafter \shStar's) light curve exhibits periodic flux dips with a period of 0.653 days.
Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
The amplitudes of the flux dips are highly stochastic and unpredictable from one event to the next 0.653 days later.
This indicates the creation and clearing of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
These unusual light curve behaviors are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
The \shStar\ system has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.

@@

\subsection{Tweaking resolutions}

We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
Also, we averaged all available spectra from the Masuda reduction to increase the signal to noise.
The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
The small difference visible between the median spectrum and the single spectrum is caused by the normalization process, but the lines appear at the same strength.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZMedian}
\end{centering}
\end{figure}

As before, we also compare the data to a BOSZ model with T=5000 K and log(g)=4.5, shown in Figure \ref{fig:mgTripletBOSZMedianW5000}.
The line ratios appear to match the BOSZ model with T=4500 K much better.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to a 4500 K BOSZ and a 5000 K BOSZ model.}\label{fig:mgTripletBOSZMedianW5000}
\end{centering}
\end{figure}
